### 2018-03-23 morus.tex
completed tex trail

\begin{figure}
  \newcommand{\M}[2]{1.65,-1.5*#1-.25-.25*#2}
  \newcommand{\C}[1]{-.1,-.25-1.5*#1}
  \renewcommand{\S}[2]{.25+.25*#2,-1.5*#1}
  \centering
  \begin{subfigure}{\textwidth}
    \begin{tikzpicture}[xscale=3, yscale=1.5, every node/.style={font=\scriptsize,inner sep=2pt}]
      \foreach \r in {0,...,3} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
      \foreach \r in {0,...,4} { \draw (\S{0}{\r}) node[above] {$S^{\r}$}; }
      \draw (\C{0}|-\S{0}{0}) node[above] {$C$};

@@

      \draw[beta]  (\C{1}) node[above left] {0} -| (\S{1}{0}) node[below right] {0}
                   (\C{1}-|\S{1}{0}) -| ([xshift=-1pt]\S{1}{1}) node[above] {0\,}
                   (\M{1}{0}) node[right] {$\beta_0$};
      \draw[alpha] ([yshift=-1.5pt]\C{1}) node[left] {8} -| (\S{2}{0}) node[above right] {\!\!13}
                   (\M{1}{1}) node[right] {$\alpha_{8,26}$};
      \draw[alpha] ([yshift=-3.0pt]\C{1}) node[below left] {26} -| ([xshift=-1pt]\S{2}{0}) node[above left] {31\!};
      \draw[gamma] (\S{1}{1}) node[above] {\,0} -- (\S{2}{1}) node[above left] {31\!\!}
                   (\S{1}{1}) ++(0,-.75) -| ([xshift=-1pt]\S{1}{4}) node[above] {0\,}
                   (\M{1}{2}) node[right] {$\gamma_0$};
      \draw[delta] (\S{1}{4}) node[above] {\,0} -- (\S{2}{4}) node[above right] {13}
                   (\S{1}{4}) ++(0,-1.0) -| ([xshift=2pt]\S{2}{2}) node[below] {0} node[black] {$\times$}
                   (\M{1}{3}) node[right] {$\delta_0$};

      \draw[beta]  (\C{2}) node[above left] {31} -| ([xshift=-1pt]\S{2}{0}) node[below left] {31\!}
                   (\C{2}-|[xshift=-1pt]\S{2}{0}) -| ([xshift=0pt]\S{2}{1}) node[below left] {31\!\!}
                   (\M{2}{0}) node[right] {$\beta_{13,31}$};
      \draw[beta]  ([yshift=-1.5pt]\C{2}) node[left] {13} -| (\S{2}{0}) node[below right] {\!\!13}
                   ([yshift=-1.5pt]\C{2}-|\S{2}{0}) -| ([xshift=1pt]\S{2}{1}) node[above] {\,\,\,13};
      \draw[alpha] ([yshift=-3.0pt]\C{2}) node[below left] {7} -| (\S{3}{0}) node[above right] {12}
                   (\M{2}{1}) node[right] {$\alpha_7$};
      \draw[gamma] ([xshift=2pt]\S{2}{1}) node[below right] {13} -- ([xshift=2pt]\S{3}{1}) node[above right] {12}
                   ([xshift=2pt]\S{2}{1}) ++(0,-.75) -| (\S{2}{4}) node[below right] {13}
                   (\M{2}{2}) node[right] {$\gamma_{13}$};

@@

      \draw (\S{4}{2}) node[above] {\normalsize weight 7};

@@

        \draw[alpha] (\M{1}{1}) node[right] {$\alpha_2$};

        \draw[beta]  (\M{2}{0}) node[right] {$\beta_7$};
        \draw[alpha] (\M{2}{1}) node[right] {$\alpha_{1,15,27}$};
        \draw[gamma] (\M{2}{2}) node[right] {$\gamma_7$};
        \draw[delta] (\M{2}{3}) node[right] {$\delta_7$};
        \draw[epsil] (\M{2}{4}) node[right] {$\varepsilon_0$};

        \draw[beta]  (\M{3}{0}) node[right] {$\beta_{6,20}$};
        \draw[alpha] (\M{3}{1}) node[right] {$\alpha_{14}$};
        \draw[gamma] (\M{3}{2}) node[right] {$\gamma_{20}$};

        \draw[beta]  (\M{4}{0}) node[right] {$\beta_{19}$};

        \draw (\S{5}{2}) node[above] {\normalsize weight 9};
      \end{scope}
    \end{tikzpicture}
    \caption{\cipher{MiniMORUS-640}}
  \end{subfigure}
  \bigskip

@@

>>>>

\begin{figure}
  \newcommand{\M}[2]{1.65,-1.5*#1-.25-.25*#2}
  \newcommand{\C}[1]{-.1,-.25-1.5*#1}
  \renewcommand{\S}[2]{.25+.25*#2,-1.5*#1}
  \centering
  \begin{subfigure}{\textwidth}
    \begin{tikzpicture}[xscale=3, yscale=1.5, every node/.style={font=\scriptsize,inner sep=2pt}]
      \begin{scope}
        \foreach \r in {0,...,3} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
        \foreach \r in {0,...,4} { \draw (\S{0}{\r}) node[above] {$S^{\r}$}; }
        \draw (\C{0}|-\S{0}{0}) node[above] {$C$};

@@

        \draw[beta]  (\C{1}) node[above left] {0} -| (\S{1}{0}) node[below right] {0}
                     (\C{1}-|\S{1}{0}) -| ([xshift=-1pt]\S{1}{1}) node[above] {0\,}
                     (\M{1}{0}) node[right] {$\beta_0$};
        \draw[alpha] ([yshift=-1.5pt]\C{1}) node[left] {8} -| (\S{2}{0}) node[above right] {\!\!13}
                     (\M{1}{1}) node[right] {$\alpha_{8,26}$};
        \draw[alpha] ([yshift=-3.0pt]\C{1}) node[below left] {26} -| ([xshift=-1pt]\S{2}{0}) node[above left] {31\!};
        \draw[gamma] (\S{1}{1}) node[above] {\,0} -- (\S{2}{1}) node[above left] {31\!\!}
                     (\S{1}{1}) ++(0,-.75) -| ([xshift=-1pt]\S{1}{4}) node[above] {0\,}
                     (\M{1}{2}) node[right] {$\gamma_0$};
        \draw[delta] (\S{1}{4}) node[above] {\,0} -- (\S{2}{4}) node[above right] {13}
                     (\S{1}{4}) ++(0,-1.25) -| ([xshift=2pt]\S{2}{2}) node[below] {0} node[black] {$\times$}
                     (\M{1}{3}) node[right] {$\delta_0$};

        \draw[beta]  (\C{2}) node[above left] {31} -| ([xshift=-1pt]\S{2}{0}) node[below left] {31\!}
                     ([xshift=-1pt]\C{2}-|\S{2}{0}) -| (\S{2}{1}) node[below left] {31\!\!}
                     (\M{2}{0}) node[right] {$\beta_{13,31}$};
        \draw[beta]  ([yshift=-1.5pt]\C{2}) node[left] {13} -| (\S{2}{0}) node[below right] {\!\!13}
                     ([yshift=-1.5pt]\C{2}-|\S{2}{0}) -| ([xshift=1pt]\S{2}{1}) node[above] {\,\,\,13};
        \draw[alpha] ([yshift=-3.0pt]\C{2}) node[below left] {7} -| (\S{3}{0}) node[above right] {12}
                     (\M{2}{1}) node[right] {$\alpha_7$};
        \draw[gamma] ([xshift=2pt]\S{2}{1}) node[below right] {13} -- ([xshift=2pt]\S{3}{1}) node[above right] {12}
                     ([xshift=2pt]\S{2}{1}) ++(0,-.75) -| (\S{2}{4}) node[below right] {13}
                     (\M{2}{2}) node[right] {$\gamma_{13}$};

@@

        \draw (\S{4}{2}) node[above] {\normalsize weight 7 (not 9)};
      \end{scope}

@@

        \draw[alpha] (\C{1}) node[left] {2} -| (\S{2}{0}) node[above right] {7}
                     (\M{1}{0}) node[right] {$\alpha_{2}$};

        \draw[beta]  (\C{2}) node[above left] {7} -| (\S{2}{0}) node[below right] {7}
                     (\C{2}-|\S{2}{0}) -| ([xshift=-1pt]\S{2}{1}) node[above] {7\,}
                     (\M{2}{0}) node[right] {$\beta_7$};
        \draw[alpha] ([yshift=-1.5pt]\C{2}) node[left] {15} -| (\S{3}{0}) node[above right] {\!20}
                     (\M{2}{1}) node[right] {$\alpha_{15,1,27}$};
        \draw[alpha] ([yshift=-3.0pt]\C{2}) node[below left] {1} -| ([xshift=-1pt]\S{3}{0}) node[above left] {6\!};
        \draw[alpha] ([yshift=-4.5pt]\C{2}) node[below] {\,\,\,\,27} -| ([xshift=-3pt]\S{3}{0}) node[below] {0\,\,};
        \draw[gamma] (\S{2}{1}) node[above] {\,7} -- (\S{3}{1}) node[above left] {6\!}
                     (\S{2}{1}) ++(0,-.75) -| ([xshift=-1pt]\S{2}{4}) node[above] {7\,}
                     (\M{2}{2}) node[right] {$\gamma_7$};
        \draw[delta] (\S{2}{4}) node[above] {\,7} -- (\S{3}{4}) node[above right] {20}
                     (\S{2}{4}) ++(0,-1.25) -| ([xshift=1pt]\S{3}{2}) node[below] {\,7}
                     (\M{2}{4}) node[right] {$\delta_7$};
        \draw[epsil] (\S{2}{2}) node[above] {0} node[black] {$\times$} -- (\S{3}{2}) node[below] {7\,}
                     (\S{2}{2}) ++(0,-1.00) -| ([xshift=-4pt]\S{3}{0}) node[above left] {0}
                     (\M{2}{3}) node[right] {$\varepsilon_0$};

        \draw[beta]  (\C{3}) node[above left] {6} -| ([xshift=-1pt]\S{3}{0}) node[below left] {6\!}
                     ([xshift=-1pt]\C{3}-|\S{3}{0}) -| (\S{3}{1}) node[below left] {6\!}
                     (\M{3}{0}) node[right] {$\beta_{20,6}$};
        \draw[beta]  ([yshift=-1.5pt]\C{3}) node[left] {20} -| (\S{3}{0}) node[below right] {\!20}
                     ([yshift=-1.5pt]\C{3}-|\S{3}{0}) -| ([xshift=1pt]\S{3}{1}) node[above] {\,\,\,\,20};
        \draw[alpha] ([yshift=-3.0pt]\C{3}) node[below left] {14} -| (\S{4}{0}) node[above right] {19}
                     (\M{3}{1}) node[right] {$\alpha_{14}$};
        \draw[gamma] ([xshift=2pt]\S{3}{1}) node[below right] {20} -- ([xshift=2pt]\S{4}{1}) node[above right] {19}
                     ([xshift=2pt]\S{3}{1}) ++(0,-.75) -| (\S{3}{4}) node[below right] {20}
                     (\M{3}{2}) node[right] {$\gamma_{20}$};

        \draw[beta]  (\C{4}) node[left] {19} -| (\S{4}{0}) node[below right] {19}
                     (\C{4}-|\S{4}{0}) -| ([xshift=2pt]\S{4}{1}) node[below right] {19}
                     (\M{4}{0}) node[right] {$\beta_{19}$};

        \draw (\S{5}{2}) node[above] {\normalsize weight 9 (not 11)};
      \end{scope}
    \end{tikzpicture}
    \caption{\cipher{MiniMORUS-640}}
  \end{subfigure}
  \bigskip

@@

\begin{figure}

  \caption{Suspicious things I'd like to verify with full \cipher{MORUS}}
\end{figure}
